---
title: "p8105_hw1_wz2675"
author: "Wenyu Zhang"
date: "2023-09-14"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(moderndive)
data("early_january_weather")
```

# Problem 1

## Part 1
Inside the dataset `early_january_weather`, there are `r ncol(early_january_weather)` variables including "`r colnames(early_january_weather)`" with `r nrow(early_january_weather)` observations. Among all the variables, we focusing on the `temperature` variable inside the dataset. We noticed that the mean temperature in this data set is `r mean(early_january_weather$temp)` degrees Fahrenheit.

## Part 2
Next we are going to make a scatter plot
```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("time_hour_vs_temp_on_humidity_scatter_plot.pdf", height = 4, width = 6)
```

We noticed that starting from January 1st to January 10th the temperature keeps steady between 20-50 degrees Fahrenheit, the humidity is also below 60 with few hours exceeding the value. Beginning from January 10th, the temperature reaches highest to 60 degrees Fahrenheit with humidity beyond 80 and drop back to 40 degrees Fahrenheit and around 60 humidity after Jan 14th.

# Problem 2

```{r}
p2_df =
  tibble(
    vec_num = rnorm(10),
    vec_log = vec_num > 0,
    vec_chr = c("one", "two", "three", "four", "five", 
                "six", "seven", "eight", "nine", "ten"),
    vec_fac = factor(c("Good", "Good", "Good", "Fair", "Fair", 
                       "Fair", "Fair", "Bad", "Bad", "Bad"))
  )
```

Now trying to calculate the mean of each variables in the data frame.

```{r}
mean(pull(p2_df, 1))
mean(pull(p2_df, 2))
mean(pull(p2_df, 3))
mean(pull(p2_df, 4))
```

We noticed that only numeric and logical vectors are able to have numeric means, which only the first columns got a result. The character and factor vector are not able to have means.

Now we turn the logical, character, and factor vectors into numeric to see if they can have mean

```{r, eval = FALSE}
num_log = as.numeric(pull(p2_df, 2))
num_chr = as.numeric(pull(p2_df, 3))
num_fac = as.numeric(pull(p2_df, 4))
```

