---
title: "p8105_hw1_wz2675"
author: "Wenyu Zhang"
date: "2023-09-14"
output: github_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(moderndive)
data("early_january_weather")
```

# Problem 1

## Part 1
Inside the dataset `early_january_weather`, there are `r ncol(early_january_weather)` variables including "`r colnames(early_january_weather)`" with `r nrow(early_january_weather)` observations. Among all the variables, I noticed that the variable "wind_gust" have many values of "NA", this might due to loss of the data in most of the time and we need to omit those NA values when we want to find a pattern regarding this variable. Moving on, we noticed that the mean temperature in this data set is `r mean(pull(early_january_weather, temp))` degrees Fahrenheit using variables `temp` to get the answer.

## Part 2
Next we are going to make a scatter plot
```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("time_hour_vs_temp_on_humidity_scatter_plot.pdf", height = 4, width = 6)
```

We noticed that starting from January 1st to January 10th the temperature keeps steady between 20-50 degrees Fahrenheit, the humidity is also below 60 with few hours exceeding the value. Beginning from January 10th, the temperature reaches highest to 60 degrees Fahrenheit with humidity beyond 80 and drop back to 40 degrees Fahrenheit and around 60 humidity after Jan 14th.

# Problem 2

```{r}
p2_df =
  tibble(
    vec_num = rnorm(10),
    vec_log = vec_num > 0,
    vec_chr = c("one", "two", "three", "four", "five", 
                "six", "seven", "eight", "nine", "ten"),
    vec_fac = factor(c("Good", "Good", "Good", "Fair", "Fair", 
                       "Fair", "Fair", "Bad", "Bad", "Bad"))
  )
```

Now trying to calculate the mean of each variables in the data frame.

```{r}
mean(pull(p2_df, 1))
mean(pull(p2_df, 2))
mean(pull(p2_df, 3))
mean(pull(p2_df, 4))
```

We noticed that only numeric and logical variables are able to have numeric means, which only the first columns got a result. The character and factor variables are not able to have means.

Now we turn the logical, character, and factor variables into numeric to see if they can have mean:

```{r, eval = FALSE}
num_log = as.numeric(pull(p2_df, 2))
num_chr = as.numeric(pull(p2_df, 3))
num_fac = as.numeric(pull(p2_df, 4))
```

After applying the `as.numeric` function, we see that the logical and factor variable can be transformed into numeric value where character variable still cannot be transformed. Moreover, although factor variables have numeric values, it cannot be used to calculate mean since the numeric value only represents different levels of the original variable. Thus, all these results shows that only numeric and logical variables can have a mean from the data frame.
